%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.4in,right=0.75in,bottom=0.6in]{geometry} % Document margins

\name{Roseanna Ferguson} % Your name
\address{Website: www.rferguson.co.uk \\ Email: fergusonroseanna@gmail.com}
 % Your phone number and email % Your address
 % Your phone number and email


\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Personal Statement}
	
	%An aptitude for understanding and solving complex problems.
	%Energy, enthusiasm, versatility and creativity.
	%Excellent communication and interpersonal skills.
	%Be passionate about computers in general and software in particular – even if you don’t have much programming experience
	%Have an exceptional knack for problem solving and logical reasoning
	%Relish a tough challenge and be eager to learn new skills
	%Be a great communicator and team player. 
	
	
I am a fourth year MMath student at the University of Warwick. Logical reasoning, basic Java and Matlab are some of the skills I gained as part of my studies. In addition, the research I am undertaking this summer shows a clear aptitude for understanding and solving complex problems.
\item My ability to use enthusiasm and creativity to succeed in a variety of organisations and roles demonstrates versatility. Public speaking and liaising duties in societies shows proven capabilities in communication. The strong interpersonal skills I possess can be demonstrated through volunteering roles such as teaching in South Africa. Finally, I am passionate about contributing to any community I belong to, displayed by my activities in Athena Swan. 

\end{rSection}
\begin{rSection}{Education}
{\bf Warwick University, UK} \hfill {\bf Oct 2012 - Jun 2016} \\ 
MMath in Mathematics \\
First Year: {\bf 76\%}, 
Second Year: {\bf 68\%},
Third Year: {\bf 87\%} \\
%Fourth Year: {\bf \%} 
Relevant modules: Programming for Scientists (Java), Maths by Computer (Matlab), Linear Algebra, Abstract Algebra, Combinatorics, Combinatorial Optimisation, Logic, Introduction to Topology
\medskip \\
{\bf Harrogate Grammar School, Harrogate, UK} \hfill {\bf Sept 2004 - Jun 2012} \\ 
A-Levels: Mathematics({\bf A*}), Further Mathematics({\bf A*}), Physics({\bf A*}), Chemistry({\bf A*}), Economics({\bf A})\\ 
AS-Levels: Additional Further Mathematics\\
GCSEs: {\bf 4 A*s} and {\bf 2 As}
\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Work Experience}

\begin{rSubsection}{Warwick University, UK}{Jun 2015 - Sept 2015}{Undergraduate Researcher}{}
\item Prepared by taking an advanced module not for credit. Contributed to publishable work in this area. 
\item Conducted research on the optimal timing decision for executives of when to exercise options given they can exert managerial effort to influence the underlying stock price.
\item Analysed and discerned unfamiliar material which developed competency in reading academic papers.
\item Summarised findings into a poster and presented to academics. Enhanced skills in Matlab and LaTeX.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Warwick Mathematics Institute, UK}{Oct 2014 - Mar 2015}{Open Day Speaker}{}
\item Researched and selected  relevant information to produce a useful presentation, promoting my department and sharing my experiences. 
\item Presented regularly to an audience of over 300 visitors and received positive feedback. 
\item Reflected on each performance and improved my presentation skills and adjusted content accordingly.
\end{rSubsection}

%-------------------------------------------------

\begin{rSubsection}{Warwick in Africa, South Africa}{Jul 2014 - Aug 2014}{Volunteer Teacher}{}
\item Taught in a township school for 6 weeks. Managed a classroom despite language and cultural barriers.
\item Prepared lessons, covered for teachers, coordinated trips and organised after school clubs.
\item Adapted to work effectively in a disorganised and unpredictable environment with limited resources.
\item Equipped teachers with new techniques and classroom activities. The class average increased by 30\%.  
\end{rSubsection}



%-------------------------------------------------

\begin{rSubsection}{Harrogate and District NHS Foundation Trust, UK}{Aug 2013}{Volunteer Auditor}{}
\item Audited a patient care pathway which involved understanding detailed information in a short time.
\item Analysed and interpreted data to report to my manager. Recommended ways to improve the implementation of the pathway. 
%\item Negotiated with the staff tactfully to find a convenient time to access medical notes and worked around their busy schedules and work environments. 
\end{rSubsection}

%------------------------------------------------

\pagebreak
\begin{rSubsection}{CCF Accountancy, UK}{Aug 2012 - Sept 2012}{Assistant Accountant}{}
\item Carried out basic accounting and bookkeeping. Covered the front desk, directly interacting with clients.
\item Communicated with clients to obtain necessary information. Gained experience with SAGE and Excel. 
\end{rSubsection}


%------------------------------------------------


\end{rSection}

%----------------------------------------------------------------------------------------
%	Positions of Responsibility
%----------------------------------------------------------------------------------------

\begin{rSection}{Positions of Responsibility}

%------------------------------------------------

\begin{rSubsection}{Athena Swan}{Mar 2014 - Current}{Undergraduate Representative}{}
	\item Organised surveys, contributed to discussions and proposed ideas to address the gender imbalance in mathematics. 
	\item Recruited other women and minorities in the undergraduate community to join Athena Swan. 
	\item Obtained funding and support from the department for weekly coffee mornings aimed at women. 
	\item Publicised, developed and led coffee mornings. Coordinated speakers, workshops, activities, discussions and a joint staff and student event.
	\item Campaigned successfully for a new position on the executive of the Warwick Mathematics Society whose role is to continue and develop these events. 
	\item Increased the ratio of male to female on the executive of Warwick Mathematics Society from 8:1 in 2014 to 3:2 in 2015, as a direct result.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Warwick Mathematics Society}{Feb 2014 - Feb 2015}{Revision Guides Editor}{}
\item Edited and printed over 20 revision guides which accumulated in over 3000 printed copies for over 800 members. Arranged the venue, advertising and logistics for the distributions of printed copies. 
\item Implemented an online request form to deal with demand and supply issues the society had experienced.
\item Expanded the position which resulted in the appointment of a second editor the following year. 
\item Contributed to all aspects of the society. In particular, provided ideas for new initiatives.
\end{rSubsection}


%------------------------------------------------
\begin{rSubsection}{Warwick Yoga Society}{Feb 2014 - Feb 2015}{Head of Class}{}
\item Liaised with the yoga instructor on matters concerning administration, replacements and remuneration.
\item Planned, promoted and ran events as part of a team such as yoga brunch and other socials.
\end{rSubsection}

\end{rSection}
%--------------------------------------------------------------------------------
\iffalse
\begin{rSection}{Achievements}

\begin{sSubsection}{}{}{}{}
\item Sixth Form Physics Cup (2012)
\item Sixth Form Mathematics Prize (2011)
\end{sSubsection}

\end{rSection}
\fi
%-------------------------------------------------------------------------------------
\begin{rSection}{Skills and Interests}
\item Computing: LaTeX (Advanced), MATLAB (Intermediate), Microsoft Excel (Intermediate), Java (Basic), HTML (Basic), CSS (Basic), Javascript (Basic). To build experience in programming I have recently made a website. This is a working progress and represents my first exposure to html/CSS/JavaScript
\item Interests: Yoga, Cooking, Reading, Rock Climbing, Badminton, Squash, Swimming, Travelling and Mentoring.
\item I hold a full, clean driving licence.

\end{rSection}
%----------------------------------------------------------------------------------------
%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Section Name}

%Section content\ldots

%\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
