%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.4in,right=0.75in,bottom=0.6in]{geometry} % Document margins

\name{Roseanna Ferguson} % Your name
\address{www.rferguson.co.uk $\diamond$ roseannaferguson@hotmail.com $\diamond$ (+44) 7591~$\cdot$~387~$\cdot$~206}
\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Personal Statement}	
Graduated from the University of Warwick with a first class Master of Mathematics and an award for outstanding academic achievement. Currently, I work on the lightends trading desk at Castleton Commodities International where I am utilising my mathematical and programming experience in quantitative analysis and trading strategies. Previously, I supported the origination team at Centrica in advising clients, offering new ideas, valuing deals and discovering opportunities.
\item Studying mathematics has refined my analytical skills and my clear aptitude for understanding and solving complex problems can be shown both by my final year project on Ergodic Theory and research using stochastic analysis applied to mathematical finance, which I carried out in my spare time. Furthermore, I continually strive to widen my experience in other technical areas such as programming. I have completed various projects including building my own website, developing a back-testing framework in MATLAB using object oriented programming and completing two online courses in machine learning.
\item My ability to use enthusiasm and creativity to succeed in a variety of organisations, despite being in pressurised situations, demonstrates versatility. Finally, I am passionate about contributing to the communities I belong to, displayed by my activities in Athena Swan and teaching in South Africa.
\end{rSection}
\begin{rSection}{Education}
	\begin{rSubsection}{\bf Warwick University}{Oct 2012 - Jun 2016}{First Class Master of Mathematics}{}
\item {\bf Master of Mathematics Prize} for outstanding academic achievement
\item First Year: {\bf 76\%}, Second Year: {\bf 68\%}, Third Year: {\bf 87\%}, Fourth Year: {\bf 89\%}
\item Relevant modules: Brownian Motion, Advanced PDEs, Bayesian Forecasting and Intervention, Probability Theory, Stochastic Processes, Dynamic Stochastic Control, Combinatorial Optimisation
\item Research Project: Ergodic Theorems For Free Groups
\end{rSubsection}
\begin{rSubsection}{Harrogate Grammar School}{Sep 2004 - Jun 2012}{Secondary School}{}
\item A-Levels: Mathematics({\bf A*}), Further Mathematics({\bf A*}), Physics({\bf A*}), Chemistry({\bf A*}), Economics({\bf A})
\item AS-Levels: Additional Further Mathematics
\item Awards included Sixth Form Physics Cup (2012), Sixth Form Mathematics Prize (2011)
%\item GCSEs: {\bf 4 A*s} and {\bf 2 As}
	\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Work Experience}
	
	\begin{rSubsection}{Castleton Commodities International}{May 2017 - Present}{Quantitative Analyst}{}
		\item Built a live refinery margin model using VBA and MATLAB with a user interface that allows easy identification of mis-pricing based on historical values. It has automatic email updates. Created a live forward blending arb model using linear programming.
		\item Provide ad-hoc analysis for the lightends trading desk on fundamentals, prices and risk. Back-test systematic trading strategies and create price data infrastructure. Develop supply and demand models and semi automated ship tracking.
		\item Built automatic processes triggered by email and a GUI in Python for automatic downloads.
		\item Identify key news in the market at pivotal points which traders can use directly to reduce risk and add value. Provide analysis and reports which are shared with traders and the management team at CCI.
		\item Experience in building business relationships in China. Manage a variety of relationships with key internal and external stakeholders. Negotiated better terms with information providers and reduced IT bottlenecks in the team. Network with the wider firm to create better information flow. 
	\end{rSubsection}	
	\newpage
	\begin{rSubsection}{Centrica}{Oct 2016 - May 2017}{Energy Marketing and Trading Analyst}{}
		\item Support sales by providing valuations, hedging strategies and fundamental market analysis.
		\item Build models in VBA which use linear optimisation and backtesting to evaluate the intrinsic value of different gas swing contracts. Analyse patterns in gas prices to find potential arbitrage opportunities.   
		\item Investigate relationships within the power markets using correlation, regression analysis and fundamental supply and demand dynamics.
		\item Used Monte Carlo simulations and distribution fitting to value the cost of a flexible gas contract.
		\item Research all aspects of emerging technologies which generate power and gas including regulations. Build business cases and find possible opportunities within these markets. 
		\item Interact with clients regularly to find bespoke solutions and network in the industry by attending conferences.  Gained understanding and experience of over the counter trading in the energy markets.	
		
	\end{rSubsection}
	

\begin{rSubsection}{Warwick University, UK}{Jun 2015 - Sep 2015}{Undergraduate Researcher}{}
\item Conducted research on the optimal timing decision for executives of when to exercise options given they can exert managerial effort to influence the underlying stock price.  
\item Presented findings to academics. Contributed to publishable work in this area.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Warwick Mathematics Institute, UK}{Oct 2014 - Mar 2015}{Open Day Speaker}{}
\item Presented regularly to an audience of over 300 visitors promoting my department. 
\end{rSubsection}

%------------------------------------------------
\begin{rSubsection}{Warwick in Africa, South Africa}{Jul 2014 - Aug 2014}{Volunteer Teacher}{}
\item Prepared and taught lessons, covered for teachers and coordinated trips and clubs. Managed a classroom despite language and cultural barriers. Adapted in an unpredictable environment with limited resources.
\item Equipped teachers with new techniques and classroom activities. The class average increased by 30\%.  
\end{rSubsection}



%-------------------------------------------------
\begin{rSubsection}{Harrogate and District NHS Foundation Trust, UK}{Aug 2013}{Volunteer Auditor}{}
\item Audited a patient care pathway. Analysed data to recommend improvements to the implementation. 
%which involved understanding detailed information in a short time.%
%\item Negotiated with the staff tactfully to find a convenient time to access medical notes and worked around their busy schedules and work environments. 
\end{rSubsection}

%------------------------------------------------
\iffalse

\begin{rSubsection}{CCF Accountancy, UK}{Aug 2012 - Sep 2012}{Assistant Accountant}{}
\item Carried out basic accounting and bookkeeping. Covered the front desk, directly interacting with clients.
\item Communicated with clients to obtain necessary information. Gained experience with SAGE and Excel. 
\end{rSubsection}

\fi

%------------------------------------------------


\end{rSection}

%----------------------------------------------------------------------------------------
%	Positions of Responsibility
%----------------------------------------------------------------------------------------

\begin{rSection}{Positions of Responsibility}

%------------------------------------------------

\begin{rSubsection}{Athena Swan}{Mar 2014 - Jun 2016}{Undergraduate Representative}{}
	%\item Organised surveys, contributed to discussions and proposed ideas to address the gender imbalance in mathematics. 
	%\item Recruited other women and minorities in the undergraduate community to join Athena Swan. 
	\item Obtained funding and support from the department for weekly coffee mornings aimed at women. 
	\item Publicised, developed and led coffee mornings. Coordinated speakers, workshops and discussions.
	\item Campaigned successfully for a new position on the executive of the Warwick Mathematics Society whose role is to continue and develop these events. 
	\item Increased the ratio of male to female on the executive of Warwick Mathematics Society from 8:1 in 2014 to 3:2 in 2015, as a direct result.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Societies}{Feb 2014 - Feb 2015}{University of Warwick}{}
\item Revision Guides Editor for Warwick Mathematics Society. Edited and printed over 20 revision guides which accumulated in over 3000 printed copies for over 800 members. Implemented an online request form to deal with demand and supply issues the society had experienced.
\item Head of Class for Warwick Yoga Society. Liaised with the yoga instructor on matters concerning administration, replacements and remuneration. Planned, promoted and ran events as part of a team such as yoga brunch and other socials.
\end{rSubsection}
\end{rSection}
%--------------------------------------------------------------------------------
\iffalse
\begin{rSection}{Achievements}

\begin{sSubsection}{}{}{}{}
\item Sixth Form Physics Cup (2012)
\item Sixth Form Mathematics Prize (2011)
\end{sSubsection}

\end{rSection}
\fi
%-------------------------------------------------------------------------------------
\begin{rSection}{Skills and Interests}
Computing: Microsoft Excel (Advanced), VBA (Advanced), MATLAB (Advanced), LaTeX (Advanced), Python (Intermediate), SQL (Intermediate), HTML (Intermediate), Java (Basic), \\
Interests: Learning Mandarin, Yoga, Cooking, Reading, Rock Climbing. \\
%Projects: To build experience in programming I have made a website. This is a work in progress and represents my first exposure to HTML/CSS/JavaScript. I have also made an option pricing programme in Java.\\


\end{rSection}
%----------------------------------------------------------------------------------------
%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Section Name}

%Section content\ldots

%\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
